---
title: "RWorksheet_Sabarillo#1"
author: "Sabarillo, Kirk Axl Dend"
date: "2024-09-16"
output: pdf_document
---
1.
```{r}
age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,
35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41,
51, 35, 24, 33, 41)

age 

length(age)

```
2.
```{r}
reciprocal_age <- 1/ age

reciprocal_age

```
3.This code creates a new vector that's an extended version of the original age vector,
with a 0 inserted in the middle.
```{r}
new_age <- c(age, 0, age)

new_age

```
4.
```{r}
sort_age <- sort(age)

sort_age

```
5.
```{r}
min_age <- min(age)

max_age <- max(age)

min_age

max_age

```
6.
```{r}
data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5, 2.3, 2.5, 2.3, 2.4, 2.7)

length(data)

data
```
7.
```{r}
doubled_data <- data * 2

doubled_data

```
As we can see here the data is multiplied by 2
8.1
```{r}
seq_1_to_100 <- 1:100

```
8.2
```{r}
seq_20_to_60 <- 20:60

```
8.3
```{r}
mean_20_to_60 <- mean(seq_20_to_60)

```
8.4
```{r}
sum_51_to_91 <- sum(51:91)

```
8.5
```{r}
seq_1_to_1000 <- 1:1000

```
a.
```{r}
numdatapoints <- length(seq_1_to_100) + length(seq_20_to_60) + 1 + 1

numdatapoints

```
b.
```{r}
seq_1_to_100; seq_20_to_60; mean_20_to_60; sum_51_to_91

```
c.
```{r}
subset_data <- seq_1_to_1000[seq_1_to_1000 <= 10]

max_value <- max(subset_data)

max_value


```
9.
```{r}
not_divisible <- Filter(function(i) { all(i %% c(3, 5, 7) != 0) }, seq(100))

not_divisible

```
10.
```{r}
seq_backwards <- seq(100, 1, by = -1)

```
11.
```{r}
multiples_3_or_5 <- Filter(function(x) { x %% 3 == 0 || x %% 5 == 0 }, seq(1, 24))

sum_multiples <- sum(multiples_3_or_5)

```
a.
```{r}
num_data_points_10_11 <- length(seq_backwards) + length(multiples_3_or_5)

```
b.
```{r}
seq_backwards; multiples_3_or_5; sum_multiples; num_data_points_10_11

```
12. The output would result into an error because
the variable x is used before it was assigned a value
```{r}

```
13.
```{r}
score <- c(72, 86, 92, 63, 88, 89, 91, 92, 75, 75, 77)

score[2]

score[3]

```
14.
```{r}
a <- c(1, 2, NA, 4, NA, 6, 7)
```
a.
```{r}
print(a, na.print = "-999")

```
b. The output displays the vector 'a' with NA values replaced by "-999"

15.
```{r}
name <- readline(prompt = "Input your name: ")

age <- readline(prompt = "Input your age: ")

print(paste("My name is",name, "and I am",age ,"years old."))

print(R.version.string)
```
The output displays the personalized message based on the user's input, 
followed by the current R version string.

