---
title: "RWorksheet_Sabarillo#4a"
author: "Sabarillo, Kirk Axl Dend"
date: "2024-10-14"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#1.
household_df <- read.csv("/cloud/project/worksheet#4/Household Data.csv")
household_df
```
1.a - The data has 28 objects with 3 variables:Shoe size, Height and Gender
```{r}
#1.b
male_subset <- subset(household_df, Gender == "M" & Shoe.size&Height)
male_subset
```

```{r}
#1.b
female_subset <- subset(household_df, Gender == "F" & Shoe.size&Height)
female_subset
```

```{r}
#1.c
mean1 <- mean(household_df$Shoe.size)
mean1
mean2 <- mean(household_df$Height)
mean2
```

1.d - Looking at the data, it's clear that the relationship between height and shoe size differs between males and females.  For males, there's a more predictable pattern where shoe size increases as height increases.  This isn't as consistent for females, where shoe size seems to vary more independently of height.
```{r}
#2.
month_vector <- c("March", "April" ,"January" ,"November" ,"January", "September","October","September","November","August","January","November","November","February","May","August","July","December","August","August","September","November","February","April")

factor_months <- factor(month_vector)
factor_months

```

```{r}
#3.
month_summary <- summary(month_vector)
month_summary
factor_month_summary <- summary(factor_months)
factor_month_summary
```

```{r}
#4.
direction_vector <- c(c("East", "West", "North"), c(1,4,3))
direction_vector
direction_matrix <- matrix(direction_vector,nrow=3,ncol=2)
direction_matrix
```


```{r}
#4.
colnames(direction_matrix) <- c("Direction", "Frequency")
direction_matrix
```

```{r}
#4.
ordered_direction_factor <- factor(direction_matrix,levels = c("East","West","North"))
print(ordered_direction_factor)
```

```{r}
#5.a
setwd("/cloud/project/worksheet#4")
strat_df <- read.table("import_march.csv", header= TRUE, sep = ",")
strat_df
```

```{r}
#5b - Because the numbers 1, 2, and 3 weren't part of the expected options in that category, R marked them as missing data (NA).
strat_df
```