---
title: "RWorksheet_Sabarillo#4c.Rmd."
author: "Sabarillo, Kirk Axl Dend"
date: "2024-11-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1.
```{r}
mpg_data <- read.csv("/cloud/project/worksheet#4/mpg.csv") 
str(mpg_data)
```

1.b - Based on the information provided, these are the categorical variables: manufacturer: The name of the car manufacturer. model: The specific model of the car. drv: The type of drive train (f = front-wheel drive, r = rear-wheel drive, 4 = 4wd). class: The type of car (e.g., compact, SUV).
```{r}
str(mpg_data)
cat_Var <- sapply(mpg_data, is.character)
cat_Var
```

1.c - These are the continuous variables in the dataset: displ: Engine displacement (in liters). year: Year of manufacture. cyl: Number of cylinders. cty: City miles per gallon. hwy: Highway miles per gallon.
```{r}
con_Var <- sapply(mpg_data, is.numeric)
con_Var

library(dplyr)
library(ggplot2)
```

2.a - model on the x-axis manufacturer on the y-axis Since both are categorical variables, the plot will show a grid of points. Each point represents a combination of a specific car model and its manufacturer.
```{r}
model_counts <- mpg_data %>%
  group_by(manufacturer) %>%
  summarise(unique_models = n_distinct(model)) %>%
  arrange(desc(unique_models))

print(model_counts)

top_manufacturer <- model_counts$manufacturer[1] 
print(paste("The manufacturer with the most models is:", top_manufacturer))
```

2.b This plot might not be very useful in its basic form. Here's why and how to improve it: Overplotting: Many car models might share the same manufacturer, leading to points overlapping and obscuring the actual count. Lack of quantitative information: The plot doesn't tell us how many cars of each model a manufacturer produces.Here are some ways to make it more informative: geom_jitter(): Instead of geom_point(), use geom_jitter() to add some random noise to the point positions, reducing overplotting. geom_count(): This geom will vary the size of the points based on how many times that model-manufacturer combination occurs. Summarize and plot counts: Create a new data frame that counts the occurrences of each model-manufacturer pair and then use geom_col() or geom_bar() to visualize the counts.
```{r}
model_counts$manufacturer <- as.factor(model_counts$manufacturer)

plot(model_counts$manufacturer, model_counts$unique_models, 
     type = "h", 
     xlab = "Manufacturer", 
     ylab = "Number of Unique Models",
     main = "Unique Models per Manufacturer")

ggplot(model_counts, aes(x = manufacturer, y = unique_models)) +
  geom_col() +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +  
  labs(x = "Manufacturer", y = "Number of Unique Models", 
       title = "Unique Models per Manufacturer")
```
3.
```{r}
top_models <- mpg_data %>% 
  count(model) %>% 
  top_n(20) %>% 
  pull(model)

top_model_data <- mpg_data %>% 
  filter(model %in% top_models)

ggplot(top_model_data, aes(x = model, y = year)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Model", y = "Year", title = "Top 20 Models and Their Years")
```
4.
```{r}
model_counts <- mpg_data %>%
  group_by(model) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

print(model_counts)
```
4.a
```{r}
ggplot(model_counts[1:20, ], aes(x = model, y = count, fill = model)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none") +  
  labs(x = "Model", y = "Count", title = "Top 20 Car Models by Count") +
  scale_fill_viridis_d()
```
4.b
```{r}
ggplot(model_counts[1:20, ], aes(x = model, y = count, fill = model)) + 
  geom_col() +
  coord_flip() + 
  theme(legend.position = "none") +  
  labs(x = "Model", y = "Count", title = "Top 20 Car Models by Count") +
  scale_fill_viridis_d()
```
5.a
```{r}
ggplot(mpg_data, aes(x = cyl, y = displ, color = displ)) +
  geom_point() +
  labs(title = "Relationship between No. of Cylinders and Engine Displacement",
       x = "Number of Cylinders (cyl)",
       y = "Engine Displacement (displ)",
       color = "Engine Displacement") + 
  scale_color_gradient(low = "blue", high = "red")
```
6.a
```{r}
traffic <- read.csv("/cloud/project/worksheet#4/traffic.csv")
str(traffic)

ggplot(mpg_data, aes(x = displ, y = hwy, color = cty)) + 
  geom_point() +
  labs(title = "Relationship between Engine Displacement, Highway MPG, and City MPG",
       x = "Engine Displacement (displ)",
       y = "Highway Miles per Gallon (hwy)",
       color = "City MPG (cty)") +
  scale_color_gradient(low = "blue", high = "red")
```
6.b
```{r}
junction <- subset(traffic, select = Junction)
head(junction)
tail(junction)
```
6.c
```{r}

library(ggplot2)
ggplot(traffic, aes(x = DateTime, y = Vehicles, color = Junction)) +
  geom_line() +
  labs(title = "Traffic Counts by Junction", x = "Date & Time", y = "Vehicles")
```
7.
```{r}
library("readxl")
alexa <- read_xlsx("/cloud/project/worksheet#4/alexa_file.xlsx")
```
7.a
```{r}
nrow(alexa)
ncol(alexa)
```
7.b
```{r}
library(dplyr)
variationTotal <- alexa %>%
  group_by(variation) %>%
  summarize(total = n())
print(variationTotal)
```
7.c
```{r}
ggplot(variationTotal, aes(x = variation, y = total, fill = variation)) +
  geom_bar(stat = "identity") +
  labs(title = "Total Variations", x = "Variation", y = "Total") +
  theme_minimal()
```
7.d
```{r}

library(dplyr)
no_of_verified_reviews <- alexa %>%
  group_by(date) %>%
  summarize(count = n()) %>%
  arrange(date)
```

```{r}
library(ggplot2)
ggplot(no_of_verified_reviews, aes(x = date, y = count)) +
  geom_line(color = "red") +
  labs(title = "Verified Reviews Over Time", x = "Date", y = "Verified Reviews") +
  theme_minimal()
```
7.e
```{r}
variationRating <- alexa %>%
  group_by(variation) %>%
  summarize(avg_rating = mean(rating, na.rm = TRUE)) %>%
  arrange(desc(avg_rating))
print(variationRating)
```

```{r}
ggplot(variationRating, aes(x = reorder(variation, avg_rating), y = avg_rating, fill = variation)) +
  geom_bar(stat = "identity") +
  labs(title = "Average Ratings by Variation", x = "Variation", y = "Average Rating") +
  coord_flip()
```


