---
title: "RWorksheet_Sabarillo#4a"
author: "Sabarillo, Kirk Axl Dend"
date: "2024-10-14"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#1.
household_df <- read.csv("/cloud/project/worksheet#4/Household Data.csv")
household_df
```
1.a - The data has 28 objects with 3 variables:Shoe size, Height and Gender
```{r}
#1.b
male_subset <- subset(household_df, Gender == "M" & Shoe.size&Height)
male_subset
```

```{r}
#1.b
female_subset <- subset(household_df, Gender == "F" & Shoe.size&Height)
female_subset
```

```{r}
#1.c
mean1 <- mean(household_df$Shoe.size)
mean1
mean2 <- mean(household_df$Height)
mean2
```

1.d - Looking at the data, it's clear that the relationship between height and shoe size differs between males and females.  For males, there's a more predictable pattern where shoe size increases as height increases.  This isn't as consistent for females, where shoe size seems to vary more independently of height.
```{r}
#2.
month_vector <- c("March", "April" ,"January" ,"November" ,"January", "September","October","September","November","August","January","November","November","February","May","August","July","December","August","August","September","November","February","April")

factor_months <- factor(month_vector)
factor_months

```

```{r}
#3.
month_summary <- summary(month_vector)
month_summary
factor_month_summary <- summary(factor_months)
factor_month_summary
```

```{r}
#4.
direction_vector <- c(c("East", "West", "North"), c(1,4,3))
direction_vector
direction_matrix <- matrix(direction_vector,nrow=3,ncol=2)
direction_matrix
```


```{r}
#4.
colnames(direction_matrix) <- c("Direction", "Frequency")
direction_matrix
```

```{r}
#4.
ordered_direction_factor <- factor(direction_matrix,levels = c("East","West","North"))
print(ordered_direction_factor)
```

```{r}
#5.a
setwd("/cloud/project/worksheet#4")
strat_df <- read.table("import_march.csv", header= TRUE, sep = ",")
strat_df
```

```{r}
#5b - Because the numbers 1, 2, and 3 weren't part of the expected options in that category, R marked them as missing data (NA).
strat_df
```

```{r}
#6.
  user_input <- readline(prompt = "Enter a number between 1 and 50: ")

  if (user_input < 1 || user_input > 50) {
    print("The number selected is below/beyond the range of 1 to 50")
  } else if (user_input == 20) {
    print("TRUE")
  } else {
    print(user_input)
  }
```

```{r}
#7.
snackPrice<-readline(prompt = "Enter Amount: ")
if (snackPrice == 50){
  print("The minimum bill is : 100")
}else if(snackPrice == 100){
  print("The minimum bill is : 100")
}else if(snackPrice == 200){
  print("The minimum bill is : 200")
}else if(snackPrice == 500){
  print("The minimum bill is : 500")
}else if(snackPrice == 1000){
  print("The minimum bill is : 1000")
}else{
  print("The number is not divisible by 50")
}
```

```{r}
# a. Create a dataframe
data <- data.frame(
  Name = c("Annie", "Thea", "Steve", "Hanna"),
  Grade1 = c(85, 65, 75, 95),
  Grade2 = c(65, 75, 55, 75),
  Grade3 = c(85, 90, 80, 100),
  Grade4 = c(100, 90, 85, 90)
)
print(data)

# b. Average score without rowMeans()
for (i in 1:nrow(data)) {
  total <- data[i, "Grade1"] + data[i, "Grade2"] + data[i, "Grade3"] + data[i, "Grade4"]
  average <- total / 4
  if (average > 90) {
    cat(data[i, "Name"], "'s average grade this semester is", average, "\n")
  }
}

# c. Tests with average score less than 80
for (j in 2:ncol(data)) {
  total <- 0
  for (i in 1:nrow(data)) {
    total <- total + data[i, j]
  }
  average <- total / nrow(data)
  if (average < 80) {
    cat("The", j - 1, "th test was difficult.\n")
  }
}

# d. Highest score without max()
for (i in 1:nrow(data)) {
  highest <- data[i, "Grade1"]
  if (data[i, "Grade2"] > highest) highest <- data[i, "Grade2"]
  if (data[i, "Grade3"] > highest) highest <- data[i, "Grade3"]
  if (data[i, "Grade4"] > highest) highest <- data[i, "Grade4"]
  if (highest > 90) {
    cat(data[i, "Name"], "'s highest grade this semester is", highest, "\n")
  }
}
```





